Identifying Equivalent State Bills through Text Reuse. \large Subtitle.

### 2015-10-13 manuscript/text_reuse.tex
updated with tasks

@@

@@

One is a data base of bill text that was extracted through the sunlight
foundation's Open States API. This data base contains approximately 500,000
bills from 2009 to 2015. From this database we will extract the bills for which we
have ground truth on policy equivalence. 
Once we obtained these bills, we will use the local alignment algorithm
implemented by (Burgess et al. 2015) in order to obtain alignment scores for
these bills. 
Information on which bills implement equivalent policies is obtained from
several sources. One option is to rely on datasets compiled by scholars who have
studied policy diffusion in the past. Another option is to rely on materials
compiled by the National Conference of State Legislatures (NCSL). The NCSL keeps
track of specific policies and regulations across states. However, the tables
compiled by the NCSL most often refer to the relevant sections in the states'
statutes instead of to the bills that these sections are based on. In order to
use these material we would have to find a way to link statute sections to their
original bills.

>>>>

\subsection{Tasks}
\begin{itemize}
\item Write paragraph about how it would be great if text-reuse could be used to classify policy overlap (BD)
\item Write paragraph on why this is not easy (FL)
\item Summarize what we do to solve problem and validate (FL)
\end{itemize}

@@

\section{Background}

\subsection{Tasks}
\begin{itemize}
\item Policy diffusion (BD get papers)
\item Text re-use in CBP in bills 
\item Text re-use in general
\begin{itemize}
\item Plaigirism
\item Alignment
\end{itemize} 
\item Discussion of text-based classification
\end{itemize}

@@

One is a data base of bill text that was extracted through the sunlight
foundation's Open States API. This data base contains approximately 500,000
bills from 2008 to 2015. From this database we will extract the bills for which we
have ground truth on policy equivalence. 
Once we obtained these bills, we will use the local alignment algorithm
implemented by (Burgess et al. 2015) in order to obtain alignment scores for
these bills. 
Information on which bills implement equivalent policies is obtained from
several sources. One option is to rely on datasets compiled by scholars who have
studied policy diffusion in the past. Another option is to rely on materials
compiled by the National Conference of State Legislatures (NCSL). The NCSL keeps
track of specific policies and regulations across states. However, the tables
compiled by the NCSL most often refer to the relevant sections in the states'
statutes instead of to the bills that these sections are based on. In order to
use these material we would have to find a way to link statute sections to their
original bills.

\subsection{Tasks}
\begin{itemize}
\item Scrape Google urls for NCSL tables (FL)
\item Extract state  \& bill \# from tables (FL)
\end{itemize}

\section{Analysis}

\subsection{Tasks}
\begin{itemize}
\item Alternative validation options (BD)
\end{itemize}
